Dotted Suffix Trees\\A Structure for Approximate Text Indexing

### 2005-08-30 paper/search.tex
s/mississipi/mississippi/

\begin{figure}
\includegraphics[width=\textwidth]{figures/mississipi-nodes}
\caption{Suffix Tree for the string \putstring{mississipi}}%
\label{fig:mississipi-nodes}
\end{figure}

To understand the pseudo-code, it is important to understand that suffix trees are normally implemented as shown in Figure~\ref{fig:mississipi-nodes} where each node contains the start and end indices of its incoming edge. When presenting the algorithm, we take the liberty of using $s+j$ where $s$ is a string and $j$ an integer to mean the suffix of $s$ starting at position $j$.

>>>>

\begin{figure}
\includegraphics[width=\textwidth]{figures/mississippi-nodes}
\caption{Suffix Tree for the string \putstring{mississippi}}%
\label{fig:mississippi-nodes}
\end{figure}

To understand the pseudo-code, it is important to understand that suffix trees are normally implemented as shown in Figure~\ref{fig:mississippi-nodes} where each node contains the start and end indices of its incoming edge. When presenting the algorithm, we take the liberty of using $s+j$ where $s$ is a string and $j$ an integer to mean the suffix of $s$ starting at position $j$.
